---
output:
  html_document:
    keep_md: yes
---

> Metabolomic network edge list generation

### Supported connections:
* structural similarity based on [pubChem CID](https://pubchem.ncbi.nlm.nih.gov/)
* biochemical connections based on [KEGG](http://www.genome.jp/kegg/)

#### See [MetaMapR](http://dgrapov.github.io/MetaMapR/) for more features.

### Examples
```{r,message=FALSE,warning=FALSE}
#devtools::install_github("dgrapov/metabomapr")
library(metabomapr)
library(dplyr)
```

### Demo data
```{r,message=FALSE,warning=FALSE}
main<-test_data() 
head(main)
```

### Convert PubChem CID to tanimoto based chemical similarity
```{r,message=FALSE,warning=FALSE}
type<-'CID'
id<-main[,type]
cid_el<-CID_tanimoto(id,as='edge.list')
head(cid_el)
```

### get KEGG based biochemical connections
```{r,message=FALSE,warning=FALSE}
type<-'KEGG'
id<-main[,type]
kegg_el<-get_KEGG_edgeList(id)
head(kegg_el)
```

### Combine edge lists using a common index
```{r,message=FALSE,warning=FALSE}
type<-'CID'
cid_el<- cid_el %>%
  convert_edgeIndex(.,start=type,end='id',db=main) %>%
  data.frame(.,cid_el %>% select(-source,-target),type=type)

type<-'KEGG'
kegg_el<- kegg_el %>%
  convert_edgeIndex(.,start=type,end='id',db=main) %>%
  data.frame(.,kegg_el %>% select(-source,-target),value=1,type=type)

#combined edge list
el<-rbind(kegg_el,cid_el)
head(el)
```

### About
* contact: createdatasol@gmail.com
* updated: `r Sys.Date()`
